---
title: "STAT0011"
output: html_notebook
---

## Question 2
### 2a)

We decided to use the DAX and CAC 40. 

First, we write a function to generate the log returns for each index:

```{r}
generate_log_returns <- function(file_name) {
	# read in the data from the csv file
  data <- read.csv(paste("./original_data/", file_name, ".csv", sep = ""))

	# convert the Price column to numeric format
	data$Price <- gsub(",", "", data$Price)
	data$Price <- as.numeric(data$Price)

	# print(data$Price[-1] - data$Price)
	a <- data$Price[-1]
	b <- data$Price[-length(data$Price)]
	print(log(b/a))

	# create a new column for log returns
	data$log_return <- c(log(data$Price[-length(data$Price)]/data$Price[-1]), 0)

	# write a new 
  return(data)
}
```

Then, we run this function on each of our datasets:
```{r results='hide'}
cac_40_log_returns <- generate_log_returns('cac_40')
dax_log_returns <- generate_log_returns('dax')
```
For example, the head of `cac_40_log_returns` looks like:
```{r}
head(cac_40_log_returns)
```
Then, we generate the weighted portfolio of our resulting datasets:
```{r, results='hide'}
# read in the data from the csv file
dax_data <- read.csv("./log_returns/dax_log_returns.csv")
cac_40_data <- read.csv("./log_returns/cac_40_log_returns.csv")

# create a new data frame for the weighted portfolio
weighted_portfolio <- data.frame(Date = dax_log_returns$Date, weighted_log_return = 0.5 * dax_data$log_return + 0.5 * cac_40_log_returns$log_return)
	
```
The head of `weighted_portfolio` looks like:
```{r}
head(weighted_portfolio)
```
Finally, we use this portfolio to calculate our 99% and 95% VaR.

First, we calculate the mean and standard deviations of the weighted log returns. 
```{r}
# calculate the distribution of the weighted log returns
portfolio_mean <- mean(weighted_portfolio$weighted_log_return)
portfolio_sd <- sd(weighted_portfolio$weighted_log_return)

# show the mean and standard deviation
cat("Mean of log returns:", portfolio_mean, "\n")
cat("Standard devision of log returns:", portfolio_sd, "\n")
```
Then, we calculate the VaRs:
```{r}
# calculate VaRs
var_99 <- - (qnorm(0.99) * portfolio_sd - portfolio_mean)
var_95 <- - (qnorm(0.95) * portfolio_sd - portfolio_mean)

# show the VaR results
cat("1-week VaR at 99% confidence level:", var_99, "or", -var_99 * 100, "percent.", "\n")
cat("1-week VaR at 99% confidence level:", var_95, "or", -var_95 * 100, "percent.", "\n")
```
